Users Guide for Corrfunc

### 2015-02-14 paper/users-guide.tex
It was impressed upon me that a data correlation function is also required. So, I am adding those as well. Means restructuring of the code directories. io has been moved one level up.
Fairly large internal re-organization for the lattice structure. In some cases, it is faster to store the positions in AVX chunks (8 for floats/4 for doubles).

\subsection{Directory Structure}
The directory structure for the code looks like this:
\dirtree{%
.1 corrfunc.
.2 paper.
.2 xi\_theory.
.3 benchmarks\DotFill
  \begin{minipage}[t]{8cm}
    IDL scripts to run benchmarks{.} 
  \end{minipage}.
.3 bin\DotFill 
  \begin{minipage}[t]{8cm}
    Will be created to copy executable files when you run `make install'{.} 
  \end{minipage}.
.3 examples\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for example C bindings using the static libraries{.} 
  \end{minipage}.
.3 include\DotFill 
  \begin{minipage}[t]{8cm}
    Header files for static libraries{.} 
  \end{minipage}.
.3 io\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for reading in data{.} 
  \end{minipage}.
.3 lib\DotFill 
  \begin{minipage}[t]{8cm}
    Will be created to copy static libraries and python library after you run `make'{.} 
  \end{minipage}.
.3 python\_bindings\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to generate python bindings{.} 
  \end{minipage}.
.3 tests\DotFill 
  \begin{minipage}[t]{8cm}
    Correct outputs for tests{.}
  \end{minipage}.
.4 data\DotFill 
  \begin{minipage}[t]{8cm}
    Mock galaxy catalogs for tests{.} 
  \end{minipage}.
.3 utils\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for creating 3-D grid and helper routines{.} 
  \end{minipage}.
.3 xi\_of\_r\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $\xi(r)${.} 
  \end{minipage}.
.3 xi\_rp\_pi\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $\xi(r_p,\pi)${.} 
  \end{minipage}.
.3 wp\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $w_p(r_p)${.} 
  \end{minipage}.
}

@@

\begin{table}
\centering
\caption{\footnotesize OpenMP scaling for the three codes. Efficiencies are defined 
as \texttt{Speedup/Nthreads}. Note, that \xir has super-linear scaling with \texttt{nthreads}.}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{cccc} 
\toprule
\multirow{2}{*}{\textbf{Nthreads}}   &
\multicolumn{3}{c}{\textbf{Efficiency[\%]}} \\
\cmidrule(l{1.0em}r{1.0em}){2-4}
&
\multicolumn{1}{c}{$\boldsymbol{\xir}$}   &
\multicolumn{1}{c}{$\boldsymbol{\xirppi}$} &
\multicolumn{1}{c}{$\boldsymbol{\wprp}$}     \\
\midrule
\input{timings_Mr19_openmp} 
\bottomrule
\end{tabular}
\end{adjustbox}
\label{table:openmp}
\end{table}

>>>>

\subsection{Directory Structure}
The directory structure for the code looks like this:
\dirtree{%
.1 corrfunc.
.2 paper.
.2 io\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for reading in data{.} 
  \end{minipage}.
.2 utils\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for creating grids and helper routines{.} 
  \end{minipage}.
.2 bin\DotFill 
  \begin{minipage}[t]{8cm}
    Will be created to copy executable files when you run `make install'{.} 
  \end{minipage}.
.2 include\DotFill 
  \begin{minipage}[t]{8cm}
    Header files for static libraries{.} 
  \end{minipage}.
.2 lib\DotFill 
  \begin{minipage}[t]{8cm}
    Will be created to copy static libraries and python library after you run `make'{.} 
  \end{minipage}.
.2 xi\_theory.
.3 benchmarks\DotFill
  \begin{minipage}[t]{8cm}
    IDL scripts to run benchmarks{.} 
  \end{minipage}.
.3 examples\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for example C bindings using the static libraries{.} 
  \end{minipage}.
.3 python\_bindings\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to generate python bindings{.} 
  \end{minipage}.
.3 tests\DotFill 
  \begin{minipage}[t]{8cm}
    Correct outputs for tests{.}
  \end{minipage}.
.4 data\DotFill 
  \begin{minipage}[t]{8cm}
    Mock galaxy catalogs for tests{.} 
  \end{minipage}.
.3 xi\_of\_r\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for getting pair-counts to compute $\xi(r)${.} 
  \end{minipage}.
.3 xi\_rp\_pi\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $\xi(r_p,\pi)${.} 
  \end{minipage}.
.3 wp\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $w_p(r_p)${.} 
  \end{minipage}.
.3 xi\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $\xi(r)$ directly on a periodic cube{.} 
  \end{minipage}.
.3 vpf\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to compute the counts-in-spheres statistic{.} 
  \end{minipage}.

.2 xi\_mocks.
.3 benchmarks\DotFill
  \begin{minipage}[t]{8cm}
    IDL scripts to run benchmarks for mocks{.} 
  \end{minipage}.
.3 examples\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for example C bindings using the static libraries for mocks{.} 
  \end{minipage}.
.3 python\_bindings\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to generate python bindings for mocks{.} 
  \end{minipage}.
.3 tests\DotFill 
  \begin{minipage}[t]{8cm}
    Correct outputs for tests for mocks{.}
  \end{minipage}.
.4 data\DotFill 
  \begin{minipage}[t]{8cm}
    Mock galaxy catalogs for tests on a sphere{.} 
  \end{minipage}.
.3 DDrppi\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for getting pair-counts to compute $\xi(r_p,\pi)$ on mocks{.} 
  \end{minipage}.
.3 wtheta\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for getting pair-counts to compute $\omega(\theta)$ {.} 
  \end{minipage}.
.3 vpf\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to compute the counts-in-spheres statistic on mocks{.} 
  \end{minipage}.
}

@@

\begin{table}
\centering
\caption{\footnotesize OpenMP scaling for the three codes. Efficiencies are defined 
as \texttt{Speedup/Nthreads}. Note, that \xir has super-linear scaling with \texttt{nthreads}
up to $\sim$ 8 threads.}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{cccc} 
\toprule
\multirow{2}{*}{\textbf{Nthreads}}   &
\multicolumn{3}{c}{\textbf{Efficiency[\%]}} \\
\cmidrule(l{1.0em}r{1.0em}){2-4}
&
\multicolumn{1}{c}{$\boldsymbol{\xir}$}   &
\multicolumn{1}{c}{$\boldsymbol{\xirppi}$} &
\multicolumn{1}{c}{$\boldsymbol{\wprp}$}     \\
\midrule
\input{timings_Mr19_openmp} 
\bottomrule
\end{tabular}
\end{adjustbox}
\label{table:openmp}
\end{table}
